---
title: "CircaPower"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{CircaPower}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CircaPower)
```


# Introduction

## Background

Circadian power calculation blalala...

## Statistical method

Insert the figure, and write the formula.

## About this tutorial

This is a tutorial for the usage of the Circapower package.
The major contents of this tutorial includes:

- Circadian power calculation (active design) when the circadian time are evenly spaced.
- A case study how to perform circadian power calculation using mouse skeletal muscle pilot data.
- Intrinsic effect size from public databases.
- Circadian power calculation given irregular circadian time distribuiton.

# About the package

## How to install the package

To install this package, start R (version "3.0" or above) and enter:

```{r, eval=FALSE}
library(devtools)
install_github("https://github.com/circaPower/CircaPower") 
```

## How to cite the package


- Wei Zong, Marianne L. Seney, Kyle D. Ketchesin, Michael T. Gorczyca, Andrew C. Liu, Karyn A. Esser, George C. Tseng*, Colleen A. McClung* and Zhiguang Huo*. Experimental Design and Power Calculation in Omics Circadian Rhythmicity Detection. (Submitted, *: co-coresponding authors)

- The manuscript can be found here: to be updated

## Maintainer

Wei Zong (wez97@pitt.edu) and Zhiguang Huo (zhuo@ufl.edu)


# Examples

## 1. Circadian power calculation (active design) when the circadian time are evenly spaced.
## 2. A case study how to perform circadian power calculation using mouse skeletal muscle pilot data.
## 3. Intrinsic effect size from public databases.
## 4. Circadian power calculation given irregular circadian time distribuiton.
